Large-scale harmonic patterns clustering

### 2010-02-26 Paper/Paper.tex
improved

Nearest neighbor for music also includes \cite{Cano2004} and ...

@@

\subsection{Setting}
We take one or two bars, normalize the patches to size 4, 8, or 16.
We roll the patch to be invariant to the key (on the patch level, not on
the song level). We learn a codebook of size $K$ over the cowbell dataset 
using the VQ algorithm (Algorithm \ref{algo:vq}). A typical learning rate 
is $0.01$ for $20$ iterations over the whole dataset.

@@

@@

>>>>

Nearest neighbor for music also includes \cite{Cano2004} and
\cite{Holzapfel2009}.

@@

\subsection{Setting}\label{ssec:setting}
We take one or two bars, normalize the patches to size 4, 8, or 16.
We roll the patch to be invariant to the key (on the patch level, not on
the song level). We learn a codebook of size $K$ over the cowbell dataset 
using the VQ algorithm (Algorithm \ref{algo:vq}). A typical learning rate 
is $0.01$ for $20$ iterations over the whole dataset.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
size & {\bf 1 bar (4)} & {\bf 2 bars (16)} & {\bf 4 beats} & {\bf 7 beats} \\ 
\hline \hline
avg. dist & 1 & 2 & 3 & 4 \\ \hline
something & 5 & 6 & 7 & 8 \\ \hline
\end{tabular}
\end{center}
\caption{{Encoding score for different pattern sizes. We can select the
size of the patterns based on bars. In this case, we put the actual size
of the pattern in parentheses. If the pattern size is based on beats, the
size is the number of beats.}}
\label{tab:psize}
\end{table}

@@

Another way is simply to present the codes in order of cluster size.
We encode the training or testing set as explained in Subsection 
\ref{ssec:setting} and we count how many patterns were closer to a particular
code than any other code. In Figure \ref{fig:firstcodes}, we show the $25$
most used codes out of a code book of size $200$.
Code from Figure \ref{fig:code} is the 37th most used code in that
code book. In Figure \ref{fig:closep}, we show a sample of patterns that
fall into its cluster.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes1}
\end{center}
\caption{{$25$ most used codes on the training set.}}
\label{fig:firstcodes}
\end{figure}

The most common pattern is a sustained note, as we can see in Figure
\ref{fig:firstcodes}. Another common pattern is a sustained note
with an harmonic, as seen in the LLE visualization (Figure \ref{fig:lle}).

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{close_patterns1}
\end{center}
\caption{{Sample of the close patterns to code in Figure \ref{fig:code}.}}
\label{fig:closep}
\end{figure}
